Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-16 paper/main.tex
update

\subsection{Frontend}

>>>>

\subsection{Frontend}
The Frontend of this project is consist of two part, for example, login page and homepage.
we can sign in with github, and then it turn to the third party authentication and the user
will ask to verify some of their user information like user github account, then we will
be redirected to A2 Inc homepage, from this website, we are able to see that A2 Inc logo
is 'do impossible', after that, it have three different regions, for example, New Zealand,
China and Middle East. which has been marked on the world map. Next, we are allowed to select
three time modes, for example, Year, Month, Day, which would determine how that line chart
perform, from the line chart we are able to see that the radiance or pixels of the sampled
regions vary in every year from 2012 to 2020, the data was based on the World Bank Nighttime
Light, and stored it in Amazon Web Services. Usually the radiance/pixels line chart is likely
to vary much more frequent from Year to Day. When mouse move to the graph, Red rectangles
is possible to turn to Red, which shows the researched area. Blue Rectangles represent some
place we chose in order to researching data.
